---
output: github_document
---

```{r echo=FALSE, message=FALSE}
knitr::opts_chunk$set(dpi = 150, message = FALSE, warning = FALSE)

library(tidyverse)
library(benelib)
library(palmerpenguins)
library(extrafont)
```


# benelib
The `benelib` contains some little helper functions for my commonly executed tasks, and thus a convenient workflow in R.

It can be downloaded, installed, and finally loaded via

```{r eval=FALSE}
remotes::install_github("benediktclaus/benelib")

library(benelib)
```


## Color schemes
There are color schemes for the PedScience Vestische Forschungs-gGmbH, the Kinderpalliativzentrum, and Deutsches Kinderschmerzzentrum in Datteln for `ggplot2`.

Those can be used via `scale_color_*` oder `scale_fill_*` and the respective name of the color scheme's institution (i.e. "pedscience", "palli", or "dksz"). By giving the argument `discrete = FALSE`, those can be mapped to continuous variables as well.

```{r}
base_plot <- ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) +
  geom_point(size = 3)
  
base_plot +
  scale_color_pedscience()
```

All of those contain six different palettes to fulfill everyone's needs. These palettes are

- `main`,
- `plaful`,
- `heat` (for heatmaps),
- `full` (which includes all colors),
- `decent`, and
- `bright`.

```{r}
base_plot +
  scale_color_pedscience(palette = "bright")

base_plot +
  scale_color_pedscience(palette = "decent")
```

## ggplot2 Theme
There is also a tailored version of ggplot2's `theme_light()`, namely `theme_bene()`, which uses Google's [Roboto font family](https://fonts.google.com/specimen/Roboto?query=Roboto).

```{r}
base_plot +
  scale_color_pedscience() +
  theme_bene()
```

For this, make sure the Roboto font (see above) is installed and the `extrafont` package is installed. After installing the font, all windows fonts need to be imported via `extrafont::font_import()` and then loaded via `extrafont::load_fonts()` once.

## R Markdown Templates
The package includes two R markdown templates for fast and easy access. There is a "Personal Template" for personal communication and "costat Page" with correct settings for working on the [Chamber of Statistics](https://benediktclaus.github.io/costat/).

These can be used via `New File` , `R Markdown...` and `From Template`.

## RStudio Project Template
To ensure a common file structure for research projects, an RStudio Project Template is also included.

This can be used via `New Project...`
