---
output: github_document
---

```{r echo=FALSE, message=FALSE}
# knitr::opts_chunk$set(dpi = 220)

library(tidyverse)
library(benelib)
```


# benelib
The `benelib` contains some little helper functions for my commonly executed tasks, and thus a convenient workflow in R.

It can be downloaded, installed, and finally loaded via

```{r eval=FALSE}
remotes::install_github("benediktclaus/benelib")

library(benelib)
```


## Color schemes
There are color schemes for the PedScience Vestische Forschungs-gGmbH, the Kinderpalliativzentrum, and Deutsches Kinderschmerzzentrum in Datteln for `ggplot2`.

Those can be used via `scale_color_*` oder `scale_fill_*` and the respective name of the color scheme's institution (i.e. "pedscience", "palli", or "dksz"). By giving the argument `discrete = FALSE`, those can be mapped to continuous variables as well.

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point(size = 3) +
  scale_color_pedscience()
```

All of those contain six different palettes to fulfill everyone's needs. These palettes are

- "main",
- "plaful",
- "heat" (for heatmaps),
- "full" (which includes all colors),
- "decent", and
- "bright".

```{r}
ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point(size = 3) +
  scale_color_pedscience(palette = "bright")

ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  geom_point(size = 3) +
  scale_color_pedscience(palette = "decent")
```

## Helper Functions
To plot means and their accompanied standard deviations, a common task in psychotherapy and medical research, is a bit of a hassle in `ggplot2`. Without computing these values yourself, you will need to use the function `stat_summary()`. This itself then uses the function `mean_sdl()` from the `MASS` package. This function, however, turns out to plot the mean and a range of 2 standard deviations above and below it by default. This can be changed with a rather lot of code

```{r}
ggplot(iris, aes(x = Species, y = Petal.Length)) +
  stat_summary(fun.data = "mean_sdl", geom = "pointrange", fun.args = list(mult = 1))
```

To simplify this, and to be sure to plot the desired range of 1 standard deviation, the function `mean_sd()` can be used.

```{r}
ggplot(iris, aes(x = Species, y = Petal.Length)) +
  stat_summary(fun.data = "mean_sd", geom = "pointrange")
```

